### 2014-08-07 Docs/mg/mg.tex
fix sectioning
nodal flow chart

\subsection{\bndryreg}

@@

>>>>

\subsubsection{\bndryreg}

@@

\item {\tt stencil\_fill\_cc\_all\_mglevels} / {\tt stencil\_fill\_cc}:
  For the nodal solver, this applies the weights to the 
  coefficients. \MarginPar{nodal does things differently than cc---need more here}

\item {\tt ml\_nd}: The main driver for the nodal multigrid.

  \item {\em recursively descend V-cycle}
\MyArrow[1em]{start3}{end3}{colorii,line width=2pt}
  \begin{itemize} 
  \item \tikzmark{end3} {\tt nodal\_smoother\_?d}: Smooth the 
    problem at the current MG level using the desired smoother.

  \item\tikzmark{start3} {\tt mg\_tower\_restriction}:  Restrict
    the defect to the coarser level by simply taking the fine value that
    lies at the same place as the coarse data.
  \end{itemize}

  \item {\em ascend V-cycle}
\MyArrow[1em]{start4}{end4}{colorii,line width=2pt}
  \begin{itemize}
  \item\tikzmark{end4} {\tt mg\_tower\_prolongation}: For nodal data, the fine grid
     will have some points at exactly the same place as the coarse data---these are
     simply copied to the fine grid.  The remain data is interpolated.

  \item\tikzmark{start4} {\tt modal\_smoother\_?d}:
  \end{itemize}
